
    \documentclass[11pt, a4paper]{letter}
    \usepackage[utf8]{inputenc}
    \usepackage{geometry}
    \usepackage{hyperref}
    \usepackage{color}
    \usepackage{xcolor}
    
    \geometry{left=1.25in, top=1in, right=1.25in, bottom=1in}
    
    \hypersetup{colorlinks=true, urlcolor=blue}
    
    \begin{document}
    
    \begin{letter}{To Whom It May Concern}
    
    \opening{Dear Sir/Madam,}
    
    [Your Name]  
[Your Address]  
[City, State, Zip]  
[Email Address]  
[Phone Number]  

[Date]  

[Employer's Name]  
[Company's Name]  
[Company's Address]  
[City, State, Zip]  

Dear [Employer's Name],

I am writing to express my interest in the .NET Developer position at [Company's Name]. With a Bachelor's degree in Software Engineering from İzmir University of Economics and extensive experience in .NET Core and SQL Server, I believe I am well-suited to contribute effectively to your team and help drive the company's success.

Throughout my career, I have cultivated a robust foundation in .NET technologies, which aligns perfectly with your requirements. My current role as an AI Data Specialist at Outlier has honed my ability to utilize reinforcement learning and prompt engineering to develop clean, scalable code. Additionally, my freelance experience as a WordPress Developer allowed me to refine my skills in creating responsive web applications, a skill set that complements your need for proficiency in HTML5, CSS3, and JavaScript.

The opportunity to work with [Company's Name] is particularly exciting to me due to your commitment to innovation and excellence in software development. Your emphasis on continuous education and professional development resonates with my career goals, as demonstrated by my completion of the .NET Core Bootcamp and the Advanced SQL Server Course from BTK Akademi. I am eager to bring my knowledge of ASP.NET Core and MVC architecture to your team and contribute to creating robust software solutions.

I am enthusiastic about the prospect of joining your team and am confident that my skills and experiences align well with the goals of [Company's Name]. I welcome the opportunity to further discuss how I can contribute to your projects and initiatives. Please feel free to contact me at your earliest convenience via email at sukru.taskiran2@gmail.com or by phone at +905426374144.

Thank you for considering my application. I look forward to the possibility of discussing this exciting opportunity with you.

Warm regards,

Şükrü Taşkıran

[Attachment: Resume]
    
    \closing{Sincerely,}
    
    \vspace{1cm}
    
    Full Name
    
    \end{letter}
    
    \end{document}
    